Mass surveillance and the lost art of keeping a secret

### 2015-06-26 paper.tex
Outlined the content
As per relevant email

\author{Theo Tryfonas\inst{1} \and Tom Crick\inst{2} \and Michael Carter\inst{3} \and Panagiotis Andriotis\inst{1}}
\institute{Cryptography Group, University of Bristol, UK etc. etc.\\
\email {t.tryfonas@bristol.ac.uk, p.andriotis@bristol.ac.uk}
\and
Cardiff Metropolitan University, xxx\\
\email{tcrick@cardiffmet.ac.uk}
\and
Canada }

@@

\section{Introduction}
\label{sec:Introduction}
xxx

>>>>

\author{Theo Tryfonas\inst{1} \and Tom Crick\inst{2} \and Michael Carter\inst{3} \and Panagiotis Andriotis\inst{1}}
\institute{Cryptography Group, University of Bristol, UK\\
\email {t.tryfonas@bristol.ac.uk, p.andriotis@bristol.ac.uk}
\and
School of Management, Cardiff Metropolitan University, UK\\
\email{tcrick@cardiffmet.ac.uk}
\and
Department of Geography, Queen's University, Toronto, Canada\\
\email{michael.carter@queensu.ca} }

@@

\section{Introduction}
\label{sec:Introduction}
Brief intro; objectives; paper outline.

\section{Background}
\label{sec:Background}
Snowden leaks and points less discussed. Scale of operations and implications for judicial oversight. Relevant legislation under consideration (e.g. the snooper's charter debate in the UK, C51 in Canada).

\section{Understanding surveillance in the context of cyberspace}
\label{sec:Understanding}
\subsection{Deconstructing State imagery of surveillance}
Metaphors and analogies for public understanding of surveillance in cyberspace. The analogy of CCTV. Wide sensing surface and algorithmic determination. Challenges from unintended consequences of bulk data collection. Algorithmic determination failures.
\subsection{The personal data dimension}
Monetisation/commoditisation of personal data resulting in casualisation of privacy rights. Unclear operating frameworks and private sector abuse of data. How it contributes to indifference and acceptance of surveillance.

\section{Co-creating viable surveillance systems}
\label{sec:Creating}
Confusion of purpose by inappropriate use of metaphors. Need to intervene earlier in the radicalisation lifecycle to debunk the propaganda messages and appeal of radicalism. Need for human-centric intelligence, open source and targeted operations.

The example of CCTV in the UK as a system-of-systems. The need for education and public understanding of surveillance tech. Implications for co-creation with the community.

\section{Conclusions}
\label{sec:Conclusions}
Abuse of power and risks of creating an unforgiving matrix.
